Individual Stellar Haloes of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-11-16 draft/paper1_v15.tex
Fix figure index in appendix

    \song{
    Massive galaxies display extended light profiles that can reach several 
    hundreds of kiloparsecs. 
    We use data from the Hyper Suprime-Cam (HSC) survey that is simultaneously wide 
    (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) to study the stellar 
    haloes of a sample of $7000$ massive galaxies at $z=0.4$. 
    The depth of the HSC data enables us to measure surface mass density profiles 
    to 100 kpc for individual galaxies without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles than smaller galaxies.  
    When this extended light is not properly accounted for (because of shallow imaging 
    and/or inadequate profile modeling), the derived stellar mass function can be 
    significantly underestimated at the high mass end.  
    Across our sample, the ellipticity of outer light profiles increases substantially 
    as we probe larger radii.  
    }
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at a later time from a series of merging events. 
    We provide surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

>>>>

    \song{
    Massive galaxies display extended light profiles that can reach several 
    hundreds of kiloparsecs. 
    We use data from the Hyper Suprime-Cam (HSC) survey that is simultaneously wide 
    (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) to study the stellar 
    haloes of a sample of ${\sim}7000$ massive galaxies at $z{\sim}0.4$. 
    The depth of the HSC data enables us to measure surface mass density profiles 
    to 100 kpc for individual galaxies without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles than smaller galaxies.  
    When this extended light is not properly accounted for (because of shallow imaging 
    and/or inadequate profile modeling), the derived stellar mass function can be 
    significantly underestimated at the high mass end.  
    Across our sample, the ellipticity of outer light profile increases substantially 
    with radius.  
    }
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at a later time from a series of merging events. 
    We provide surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.
